Multilevel spin models in cold atomic systems

### 2021-04-15 sun_phases/spin_model_paper/main.tex
added appendix on three-laser drive with complex amplitudes other minor changes to text

External fields or additional interactions that respect permutational symmetry can induce nontrivial dynamics within the PS manifold.
Even if additional Hamiltonian terms break permutational symmetry, as long as the coupling to states outside of the PS manifold is small (compared to the energy gap $U$) these terms can be restricted to the PS manifold perturbatively (see Appendix \ref{sec:pert_theory}) \cite{bravyi2011schrieffer}.
Simulating dynamics within the PS manifold requires calculating matrix elements $\bk{\ell|\O|m}$ of spin operators $\O$ with respect to PS states $\ket\ell,\ket{m}$; we discuss this calculation in Appendix \ref{sec:PS_ops}.

@@

Of course, spin-orbit coupling cannot be ``gauged away'' entirely.
Making a gauge transformation to simplify the drive comes at the cost of making kinetic energy spin-dependent, taking
\begin{align}
  H_{\t{kin}} \to H_{\t{kin}}^{(\phi)}
  \equiv -J \sum_q \cos\p{q+\mu\phi} s_{\mu\mu q},
\end{align}
as visualized in Figure \ref{fig:soc_panels}.
To better interpret this Hamiltonian, we can write it in the simplified form
\begin{align}
  H_{\t{kin}}^{(\phi)}
  = -J \sum_q
  \sp{\cos\p{q} w_{+,q}^{(\phi)} - \sin\p{q} w_{+,q}^{(\phi)}},
\end{align}
where
\begin{align}
  w_{+,q}^{(\phi)} &\equiv \sum_\mu \cos\p{\mu\phi} s_{\mu\mu q}, \\
  w_{-,q}^{(\phi)} &\equiv \sum_\mu \sin\p{\mu\phi} s_{\mu\mu q}.
\end{align}
For two-level spins, $w_{+,q}^{(\phi)}$ is proportional to the identity operator, and $w_{+,q}^{(\phi)}=2\sin\p{\phi/2} s_{q,\z}$, where $s_{\z,q}=\sum_\mu \mu\, s_{\mu\mu q}$ is a spin-$z$ operator for spin $q$, so the kinetic Hamiltonian in the gauged frame describes a (synthetic) inhomogeneous magnetic field:
\begin{align}
  \left. H_{\t{kin}}^{(\phi)} \right|_{n=2}
  = 2\sin\p{\phi/2} J \sum_q \sin\p{q} s_{\z,q}.
\end{align}
When $n>2$, an inhomogeneous magnetic field is likewise recovered in the limit of weak SOC, $s\phi\ll1$, in which case
\begin{align}
  \left. H_{\t{kin}}^{(\phi)} \right|_{s\phi\ll1}
  = J\phi \sum_q \sin\p{q} s_{\z,q} + O\p{(s\phi)^2}.
\end{align}
As the strength of SOC is increased, this Hamiltonian acquires terms with higher powers of $s_{\z,q}$, up to $s_{\z,q}^{n-1}$.

@@

In order to make the drive Hamiltonian in Eq.~\eqref{eq:drive_full} more tractable, we orient the lattice along the $z$ axis, $\v\ell=(0,0,1)$, and consider a three-laser drive with a geometry sketched in Figure \ref{fig:3LD}.
In this setup, two counter-propagating right-circularly polarized lasers point along $\v v_\pm=\pm(0,-\sin\theta,\cos\theta)$, at an angle $\theta$ to the lattice axis, and a third linearly-polarized laser points along $\v v_0=(1,0,0)$.
Choosing $\v v_+$ as the spin quantization axis, we can define new drive amplitudes $\Omega_0\equiv-(\Omega_{\v v_0,+}+\Omega_{\v v_0,-})$ and $\Omega_\pm\equiv\pm\Omega_{\v v_\pm,+}$, as well as a SOC angle $\phi\equiv\kappa\v v_+\c\v\ell=\kappa\cos\theta$, in terms of which the drive Hamiltonian becomes
\begin{align}
  H_{\t{3LD}}^{\t{full}}
  = \sum_{j,m} \Omega_m
  \p{e^{-\i m\phi j} s_{mj} \otimes\op{\e}{\g}_j + \t{h.c.}}
  + \Delta N_\e,
\end{align}
where $m\in\set{+1,0,-1}$ indexes the laser pointing along $\v v_m$; and $s_{0,j}\equiv s_{\z,j}$ for shorthand.
In the far-detuned limit $\abs{\Delta}\gg\abs{\Omega_m}$, a second-order perturbative treatment of electronic excitations ($\ket\e$) yields an effective drive Hamiltonian that only addresses ground-state nuclear spins.
After a gauge transformation $c_{j\mu}^\dag\to e^{\i\phi\mu j} c_{j\mu}^\dag$ (equivalently $s_{mj}\to e^{\i m\phi j}s_{mj}$), we can then make the simplifying assumption that all $\Omega_m$ are real to write
\begin{align}
  H_{\t{3LD}} = \sum_j H_{\t{3LD},j}^{\t{single}},
  \label{eq:drive_all}
\end{align}
where $H_{\t{3LD},j}^{\t{single}}$ denotes the action of $H_{\t{3LD}}^{\t{single}}$ on spin $j$:
\begin{multline}
  H_{\t{3LD}}^{\t{single}}
  = \tilde\Omega_+ \tilde\Omega_- s_\z
  + \tilde\Omega_0 \tilde\Omega_- s_\x
  + \tilde\Omega_0 \tilde\Omega_+ \p{s_\z s_\x  + s_\x s_\z} \\
  - \tilde\Omega_0^2 s_\z^2 - \tilde\Omega_+^2 s_\x^2
  - \tilde\Omega_-^2 s_\y^2,
  \label{eq:drive_single}
\end{multline}
with
\begin{align}
  \tilde\Omega_0 \equiv -\f{\Omega_0}{\sqrt\Delta},
  &&
  \tilde\Omega_\pm \equiv \f{\Omega_+\pm\Omega_-}{\sqrt\Delta}.
\end{align}

@@

To investigate these behaviors quantitatively, we examine time-averaged observables of the form
\begin{align}
  \bbk{\O}_\MF = \lim_{T\to\infty} \f1T \int_0^T \dd t \bk{\O\p{t}}_\MF,
\end{align}
where $\bk{\O\p{t}}_\MF$ is the mean-field value of observable $\O$ at time $t$ (see Appendices \ref{sec:MFT} and \ref{sec:bosons} for details about our mean-field simulations).
Specifically, we consider the time-averaged magnetization
\begin{align}
  \sigma_\MF \equiv \abs{\bbk{\vec\sigma}_\MF},
  &&
  \vec\sigma \equiv \f1{Ns} \times \p{S_\x,S_\y,S_\z},
\end{align}
where $S_\alpha \equiv \sum_q s_{\alpha,q}$, and the time-averaged interaction energy
\begin{align}
  \bbk{\ss}_\MF = \f1{N^2} \times \bbk{\v S\c\v S}_\MF.
\end{align}
By design, these non-negative quantities are normalized to a maximal value of one, independent of the system size $N$ or spin dimension $n$.
In the remainder of this section we will assume that $n$ is even, both for the sake of experimental relevance (most relevant atomic nuclei are fermionic) and to avoid complications from parity effects.

@@

In the weak-field limit $J\phi/U\to0$, the spin-locking $\v S\c\v S$ interactions of the spin Hamiltonian $H_\spin$ energetically restrict dynamics to the permutationally symmetric (PS) manifold.
At second order in perturbation theory, the effective spin Hamiltonian within the PS manifold becomes (see Appendix \ref{sec:pert_theory})
\begin{align}
  H_\spin^\eff
  = \f{\p{J\phi}^2}{2\p{N-1}U}
  \times \sp{S_\z^2 - N\sum_q s_{\z,q}^2},
  \label{eq:H_spin_eff}
\end{align}
whose mean-field version is
\begin{align}
  H_\MF^\eff = -\f{\p{J\phi}^2}{2U} \sum_q s_{\z,q}^2,
\end{align}
where we have used the fact that the axial magnetizations $\bk{s_{\z,q}}=\frac1N\bk{S_\z}$ within the PS manifold, and the initial value of $\bk{S_\z}=0$ is conserved by $H_\spin$.
The weak-field effective Hamiltonian preserves permutational symmetry, so $\bbk{\ss}_\MF\to1$ as $J\phi/U\to0$.
Moreover, both the spin Hamiltonian $H_\spin$ and the initial state $\ket\X$ are invariant (up to global phase) under the action of $\Pi_\z R_\x^\pi$, where $R_\x^\theta \equiv e^{-\i\theta S_\x}$ is a rotation about the $x$ axis by $\theta$ and $\Pi_\z\equiv\sum_{q>0}\v s_q\c\v s_{-q}$ is a permutation of spins $q\leftrightarrow-q$\footnote{$\Pi_\z$ can also be thought of a reflection operator that inverts momentum along the $z$ axis.}, which is to say that
\begin{align}
  e^{-\i t H_\spin} \ket\X
  &\simeq \p{\Pi_\z R_\x^\pi e^{-\i t H_\spin} {R_\x^\pi}^\dag \Pi_\z^\dag} \Pi_\z R_\x^\pi \ket\X
  \label{eq:sym_x_start} \\
  &\simeq \Pi_\z R_\x^\pi e^{-\i t H_\spin} \ket\X,
\end{align}
so
\begin{align}
  \bk{S_\y}
  = \bk{{R_\x^\pi}^\dag \Pi_\z^\dag S_\y \Pi_\z R_\x^\pi}
  = -\bk{S_\y} = 0
  \label{eq:sym_x_end}
\end{align}
at all times.
Conservation of $\bk{S_\y}=\bk{S_\z}=0$ and permutational symmetry together imply that the magnetization $\sigma_\MF$ is determined by the time-average of $\sigma_\x\equiv s_\x/s$ for a single spin:
\begin{align}
  \lim_{J\phi/U\to0} \sigma_\MF
  = \abs{\lim_{T\to\infty} \f1T \int_0^T \dd\tau
  \bk{\x|\sigma_\x\p{\tau}|\x}},
\end{align}
where
\begin{align}
  \sigma_\x\p{\tau} = e^{\i\tau s_\z^2} \sigma_\x e^{-\i\tau s_\z^2}.
\end{align}
By mapping the Hilbert space of an $n$-level spin onto the PS (Dicke) manifold of $n-1$ spin-$\frac12$ particles, we can adapt exact analytical results for the Ising model \cite{foss-feig2013nonequilibrium}\footnote{See Appendix K of Ref.~\cite{perlin2020shorttime} for a simpler adaptation of the analytics in Ref.~\cite{foss-feig2013nonequilibrium} to the one-axis twisting model $H_{\t{OAT}}=\chi s_\z^2$.} to find that
\begin{align}
  \bk{\x|\sigma_\x\p{\tau}|\x} = \p{\cos\tau}^{n-2},
\end{align}
so for even $n$
\begin{align}
  \lim_{J\phi/U\to0} \sigma_\MF
  = \f1{2\pi} \int_0^{2\pi} \dd\tau \p{\cos\tau}^{n-2}
  = \gamma\p{\f{n}{2}}.
\end{align}
When going beyond mean-field theory, correlations induced by $S_\z^2$ in Eq.~\eqref{eq:H_spin_eff} will cause $\bk{S_\x}$ to decay on time scales that diverge as $N\to\infty$, so the mean-field magnetization $\sigma_\MF$ should be interpreted as the ``intermediate-time-average'' of $\vec\sigma$.

@@

Unlike Figure \ref{fig:mean_mag_int_X} (for $\ket\X$), Figure \ref{fig:mean_mag_int_XX} (for $\ket\XX$) exhibits no sharp transition between distinct dynamical phases: the time-averaged magnetization $\sigma_\MF=0$ for all values of the field $J\phi/U$, and the interaction energy $\bbk{\ss}_\MF$ smoothly crosses over from a maximal value of 1 to a minimal value of $2\gamma\p{n}$.
The minimal value of $\bbk{\ss}_\MF$ approached as $J\phi/U\to\infty$ can be explained with arguments identical to those above and below Eq.~\eqref{eq:lim_ss}, which now imply that
\begin{align}
  \lim_{J\phi/U\to\infty} \bbk{\ss}_\MF
  = \Tr\sp{\p{\diag\op{\xx}}^2}
  = 2\gamma\p{n}.
\end{align}
The vanishing magnetization $\sigma_\MF=0$ in Figure \ref{fig:mean_mag_int_XX} is protected by symmetries of $H_\spin$ and $\ket\XX$.
For all initial states that we have considered, the value of $\bk{S_\z}=0$ is conserved by the spin Hamiltonian $H_\spin$.
Moreover, both the spin Hamiltonian $H_\spin$ and the state $\ket\XX$ are invariant (up to global phase) under the action of $R_\z^\pi$, where $R_\z^\theta\equiv e^{-\i\theta S_\z}$.
Similarly to Eqs.~\eqref{eq:sym_x_start}--\eqref{eq:sym_x_end}, this symmetry implies that
\begin{align}
  &\bk{S_\x} = \bk{{R_\z^\pi}^\dag S_\x R_\z^\pi} = -\bk{S_\x} = 0, \\
  &\bk{S_\y} = \bk{{R_\z^\pi}^\dag S_\y R_\z^\pi} = -\bk{S_\y} = 0
\end{align}
at all times, so altogether $\sigma_\MF=0$.

@@

Here we work out a general perturbation theory for SU($n$) ferromagnets with a gapped permutationally symmetric (PS) manifold.
We begin with an SU($n$)-symmetric interaction Hamiltonian of the form
\begin{align}
  H_0 = \sum_{i<j} g_{ij} \, \Pi_{ij},
  &&
  \Pi_{ij} \equiv \v s_i\c\v s_j
  = \sum_{\mu,\nu} s_{\mu\nu i} s_{\nu\mu j},
  \label{eq:H_0}
\end{align}
where $g_{ij}$ are (real) scalar coefficients for the permutation operators $\Pi_{ij}$, and $s_{\mu\nu i}\equiv c_{\mu i}^\dag c_{\nu i}$ is a transition operator for spin $i$.
We can then consider the addition of, for example, an inhomogeneous magnetic field or Ising couplings,
\begin{align}
  H_{\t{field}} = \sum_i B_i s_{\z,i},
  &&
  H_{\t{Ising}} = \sum_{i\ne j} J_{ij} s_{\z,i} s_{\z,j},
  \label{eq:field_ising}
\end{align}
or more generally an $M$-body operator
\begin{align}
  \O\p{w,X} = \sum_{k\in\D_N\p{M}} w_k X_k,
\end{align}
where $w$ is a dimension-$M$ (i.e.~$M$-index) tensor of scalar
coefficients $w_k\equiv w_{k_1k_2\cdots k_M}$; $X$ is an $M$-spin
operator, e.g.~$s_\z\otimes s_\z$ in the case of Ising interactions
with $M=2$; $k\equiv\p{k_1,k_2,\cdots,k_M}$ is a list of the
individual spins $k_i\in\ZZ_N\equiv\set{1,2,\cdots,N}$ that the operator $X_k\equiv X_{k_1k_2\cdots k_M}$ acts on; and
\begin{align}
  \D_N\p{M} \equiv
  \set{ k \in \ZZ_N^M : \t{all entries $k_i$ of $k$ are distinct} },
\end{align}
is the strictly ``off-diagonal'' part of $\ZZ_N^M$, which is necessary to identify for a consistent definition of $X_k$ as an $M$-body operator.
In this notation, the magnetic field and Ising Hamiltonians in Eq.~\eqref{eq:field_ising} respectively become $\O\p{B,s_{\z}}$ and $\O\p{J,s_\z\otimes s_\z}$.

@@

>>>>

External fields or additional interactions that respect permutational symmetry can induce nontrivial dynamics within the PS manifold.
Even if additional Hamiltonian terms break permutational symmetry, as long as the coupling to states outside of the PS manifold is small compared to the interaction energy $U$, these terms can be restricted to the PS manifold perturbatively (see Appendix \ref{sec:pert_theory}) \cite{bravyi2011schrieffer}.
Simulating dynamics within the PS manifold requires calculating matrix elements $\bk{\ell|\O|m}$ of spin operators $\O$ with respect to PS states $\ket\ell,\ket{m}$; we discuss this calculation in Appendix \ref{sec:PS_ops}.

@@

Of course, spin-orbit coupling cannot be ``gauged away'' entirely.
Making a gauge transformation to simplify the drive comes at the cost of making kinetic energy spin-dependent, taking
\begin{align}
  H_{\t{kin}} \to H_{\t{kin}}^{(\phi)}
  \equiv -J \sum_q \cos\p{q+\mu\phi} s_{\mu\mu q},
\end{align}
as visualized in Figure \ref{fig:soc_panels}.
To better interpret this Hamiltonian, we can write it in the form
\begin{align}
  H_{\t{kin}}^{(\phi)}
  = -J \sum_q
  \sp{\cos\p{q} w_{+,q}^{(\phi)} - \sin\p{q} w_{+,q}^{(\phi)}},
\end{align}
where
\begin{align}
  w_{+,q}^{(\phi)} &\equiv \sum_\mu \cos\p{\mu\phi} s_{\mu\mu q}, \\
  w_{-,q}^{(\phi)} &\equiv \sum_\mu \sin\p{\mu\phi} s_{\mu\mu q}.
\end{align}
For two-level spins, $w_{+,q}^{(\phi)}$ is proportional to the identity operator, and $w_{+,q}^{(\phi)}=2\sin\p{\phi/2} s_{\z,q}$, where $s_{\z,q}=\sum_\mu \mu\, s_{\mu\mu q}$ is a spin-$z$ operator for spin $q$, so the kinetic Hamiltonian in the gauged frame describes a (synthetic) inhomogeneous magnetic field:
\begin{align}
  \left. H_{\t{kin}}^{(\phi)} \right|_{n=2}
  = 2\sin\p{\phi/2} J \sum_q \sin\p{q} s_{\z,q}.
\end{align}
When $n>2$, an inhomogeneous magnetic field is likewise recovered in the limit of weak SOC, $s\phi\ll1$, in which case
\begin{align}
  \left. H_{\t{kin}}^{(\phi)} \right|_{s\phi\ll1}
  = J\phi \sum_q \sin\p{q} s_{\z,q} + O\p{(s\phi)^2}.
\end{align}
As the strength of SOC is increased, this Hamiltonian acquires terms with higher powers of $s_{\z,q}$, up to $s_{\z,q}^{n-1}$.

@@

In order to make the drive Hamiltonian in Eq.~\eqref{eq:drive_full} more tractable, we orient the lattice along the $z$ axis, $\v\ell=(0,0,1)$, and consider a three-laser drive with a geometry sketched in Figure \ref{fig:3LD}.
In this setup, two counter-propagating right-circularly polarized lasers point along $\v v_\pm=\pm(0,-\sin\theta,\cos\theta)$, at an angle $\theta$ to the lattice axis, and a third linearly-polarized laser points along $\v v_0=(1,0,0)$.
Choosing $\v v_+$ as the spin quantization axis, we can define new drive amplitudes $\Omega_0\equiv-(\Omega_{\v v_0,+}+\Omega_{\v v_0,-})$ and $\Omega_\pm\equiv\pm\Omega_{\v v_\pm,+}$, as well as a SOC angle $\phi\equiv\kappa\v v_+\c\v\ell=\kappa\cos\theta$, in terms of which the drive Hamiltonian becomes
\begin{align}
  H_{\t{3LD}}^{\t{full}}
  = \sum_{j,m} \Omega_m
  \p{e^{-\i m\phi j} s_{mj} \otimes\op{\e}{\g}_j + \t{h.c.}}
  + \Delta N_\e,
\end{align}
where $m\in\set{+1,0,-1}$ indexes the laser pointing along $\v v_m$; and $s_{0,j}\equiv s_{\z,j}$ for shorthand.
In the far-detuned limit $\abs{\Delta}\gg\abs{\Omega_m}$, a second-order perturbative treatment of electronic excitations ($\ket\e$) yields an effective drive Hamiltonian that only addresses ground-state nuclear spins.
After additionally making the gauge transformation $c_{j\mu}^\dag\to e^{\i\phi\mu j} c_{j\mu}^\dag$ (equivalently $s_{mj}\to e^{\i m\phi j}s_{mj}$), the drive Hamiltonian then becomes
\begin{align}
  H_{\t{3LD}} = \sum_j H_{\t{3LD},j}^{\t{single}},
  \label{eq:drive_all}
\end{align}
where $H_{\t{3LD},j}^{\t{single}}$ denotes the action of $H_{\t{3LD}}^{\t{single}}$ on spin $j$:
\begin{multline}
  H_{\t{3LD}}^{\t{single}}
  = \tilde\Omega_+ \tilde\Omega_- s_\z
  + \tilde\Omega_0 \tilde\Omega_- s_\x
  + \tilde\Omega_0 \tilde\Omega_+ \p{s_\z s_\x  + s_\x s_\z} \\
  - \tilde\Omega_0^2 s_\z^2 - \tilde\Omega_+^2 s_\x^2
  - \tilde\Omega_-^2 s_\y^2,
  \label{eq:drive_single}
\end{multline}
with
\begin{align}
  \tilde\Omega_0 \equiv -\f{\Omega_0}{\sqrt\Delta},
  &&
  \tilde\Omega_\pm \equiv \f{\Omega_+\pm\Omega_-}{\sqrt\Delta},
\end{align}
where we have made the simplifying assumption that all drive amplitudes are real to arrive at the form of $H_{\t{3LD}}^{\t{single}}$ in Eq.~\eqref{eq:drive_single}.
We relax the assumption of real drive amplitudes in Appendix \ref{sec:full_drive}.

@@

To investigate these behaviors quantitatively, we examine time-averaged observables of the form
\begin{align}
  \bbk{\O}_\MF = \lim_{T\to\infty} \f1T \int_0^T \dd t \bk{\O\p{t}}_\MF,
\end{align}
where $\bk{\O\p{t}}_\MF$ is the mean-field value of observable $\O$ at time $t$ (see Appendices \ref{sec:MFT} and \ref{sec:bosons} for details about our mean-field simulations).
Specifically, we consider the time-averaged magnetization
\begin{align}
  \sigma_\MF \equiv \abs{\bbk{\vec\sigma}_\MF},
  &&
  \vec\sigma \equiv \f1{Ns} \times \p{S_\x,S_\y,S_\z},
\end{align}
where $S_\alpha \equiv \sum_q s_{\alpha,q}$, and the time-averaged (dimensionless) interaction energy
\begin{align}
  \bbk{\ss}_\MF = \f1{N^2} \times \bbk{\v S\c\v S}_\MF.
\end{align}
By design, these non-negative quantities are normalized to lie on the interval $[0,1]$, independent of the system size $N$ or spin dimension $n$.
In the remainder of this section we will assume that $n$ is even, both for the sake of experimental relevance (most relevant atomic nuclei are fermionic) and to avoid complications from parity effects.

@@

In the weak-field limit $J\phi/U\to0$, the spin-locking $\v S\c\v S$ interactions of the spin Hamiltonian $H_\spin$ energetically restrict dynamics to the permutationally symmetric (PS) manifold.
At second order in perturbation theory, the effective spin Hamiltonian within the PS manifold becomes (see Appendix \ref{sec:pert_theory})
\begin{align}
  H_\spin^\eff
  = \f{\p{J\phi}^2}{2\p{N-1}U}
  \times \sp{S_\z^2 - N\sum_q s_{\z,q}^2},
  \label{eq:H_spin_eff}
\end{align}
whose mean-field version is
\begin{align}
  H_\MF^\eff = -\f{\p{J\phi}^2}{2U} \sum_q s_{\z,q}^2,
\end{align}
where we have used the fact that the axial magnetizations $\bk{s_{\z,q}}=\frac1N\bk{S_\z}$ within the PS manifold, and the initial value of $\bk{S_\z}=0$ is conserved by $H_\spin$.
The weak-field effective Hamiltonian preserves permutational symmetry, so $\bbk{\ss}_\MF\to1$ as $J\phi/U\to0$.
Moreover, both the spin Hamiltonian $H_\spin$ and the initial state $\ket\X$ are invariant (up to global phase) under the action of $\Pi_\z R_\x^\pi$, where $R_\x^\theta \equiv e^{-\i\theta S_\x}$ is a rotation about the $x$ axis by $\theta$ and $\Pi_\z\equiv\sum_{q>0}\v s_q\c\v s_{-q}$ is a permutation of spins $q\leftrightarrow-q$\footnote{$\Pi_\z$ can also be thought of a reflection operator that inverts momentum along the $z$ axis.}, which is to say that
\begin{align}
  e^{-\i t H_\spin} \ket\X
  &\simeq \p{\Pi_\z R_\x^\pi e^{-\i t H_\spin} {R_\x^\pi}^\dag \Pi_\z^\dag} \Pi_\z R_\x^\pi \ket\X
  \label{eq:sym_x_start} \\
  &\simeq \Pi_\z R_\x^\pi e^{-\i t H_\spin} \ket\X,
\end{align}
so
\begin{align}
  \bk{S_\y}
  = \bk{{R_\x^\pi}^\dag \Pi_\z^\dag S_\y \Pi_\z R_\x^\pi}
  = -\bk{S_\y} = 0
  \label{eq:sym_x_end}
\end{align}
at all times.
Conservation of $\bk{S_\y}=\bk{S_\z}=0$ and permutational symmetry together imply that the magnetization $\sigma_\MF$ is determined by the time-average of $\sigma_\x\equiv s_\x/s$ for a single spin:
\begin{align}
  \lim_{J\phi/U\to0} \sigma_\MF
  = \abs{\lim_{T\to\infty} \f1T \int_0^T \dd\tau
  \bk{\x|\sigma_\x\p{\tau}|\x}},
\end{align}
where
\begin{align}
  \sigma_\x\p{\tau} = e^{\i\tau s_\z^2} \sigma_\x e^{-\i\tau s_\z^2}.
\end{align}
By mapping the Hilbert space of an $n$-level spin onto the PS (Dicke) manifold of $n-1$ spin-$\frac12$ particles, we can adapt exact analytical results for the Ising model \cite{foss-feig2013nonequilibrium}\footnote{See Appendix K of Ref.~\cite{perlin2020shorttime} for a simpler adaptation of the analytics in Ref.~\cite{foss-feig2013nonequilibrium} to the one-axis twisting model $H_{\t{OAT}}=\chi s_\z^2$.} to find that
\begin{align}
  \bk{\x|\sigma_\x\p{\tau}|\x} = \p{\cos\tau}^{n-2},
\end{align}
so for even $n$
\begin{align}
  \lim_{J\phi/U\to0} \sigma_\MF
  = \f1{2\pi} \int_0^{2\pi} \dd\tau \p{\cos\tau}^{n-2}
  = \gamma\p{\f{n}{2}}.
\end{align}
When going beyond mean-field theory, inter-spin correlations generated by $S_\z^2$ in Eq.~\eqref{eq:H_spin_eff} will cause $\bk{S_\x}$ to decay on time scales that diverge as $N\to\infty$, so the mean-field magnetization $\sigma_\MF$ should be interpreted as an ``intermediate-time-average'' of $\vec\sigma$.

@@

Unlike Figure \ref{fig:mean_mag_int_X} (for $\ket\X$), Figure \ref{fig:mean_mag_int_XX} (for $\ket\XX$) exhibits no sharp transition between distinct dynamical phases: the time-averaged magnetization $\sigma_\MF=0$ for all values of the field $J\phi/U$, and the interaction energy $\bbk{\ss}_\MF$ smoothly crosses over from a maximal value of 1 to a minimal value of $2\gamma\p{n}$.
The minimal value of $\bbk{\ss}_\MF$ approached as $J\phi/U\to\infty$ can be explained with arguments identical to those in the paragraph containing Eq.~\eqref{eq:lim_ss}, which now imply that
\begin{align}
  \lim_{J\phi/U\to\infty} \bbk{\ss}_\MF
  = \Tr\sp{\p{\diag\op{\xx}}^2}
  = 2\gamma\p{n}.
\end{align}
The vanishing magnetization $\sigma_\MF=0$ in Figure \ref{fig:mean_mag_int_XX} is protected by symmetries of $H_\spin$ and $\ket\XX$.
For all initial states that we have considered, the value of $\bk{S_\z}=0$ is conserved by the spin Hamiltonian $H_\spin$.
Moreover, both the spin Hamiltonian $H_\spin$ and the state $\ket\XX$ are invariant (up to global phase) under the action of $R_\z^\pi$, where $R_\z^\theta\equiv e^{-\i\theta S_\z}$.
Similarly to Eqs.~\eqref{eq:sym_x_start}--\eqref{eq:sym_x_end}, this symmetry implies that
\begin{align}
  &\bk{S_\x} = \bk{{R_\z^\pi}^\dag S_\x R_\z^\pi} = -\bk{S_\x} = 0, \\
  &\bk{S_\y} = \bk{{R_\z^\pi}^\dag S_\y R_\z^\pi} = -\bk{S_\y} = 0
\end{align}
at all times, so altogether $\sigma_\MF=0$.

@@

Here we work out a general perturbation theory for SU($n$) ferromagnets with a gapped permutationally symmetric (PS) manifold.
We begin with an SU($n$)-symmetric interaction Hamiltonian of the form
\begin{align}
  H_0 = \sum_{i<j} g_{ij} \, \Pi_{ij},
  &&
  \Pi_{ij} \equiv \v s_i\c\v s_j
  = \sum_{\mu,\nu} s_{\mu\nu i} s_{\nu\mu j},
  \label{eq:H_0}
\end{align}
where $g_{ij}$ are (real) scalar coefficients for the permutation operators $\Pi_{ij}$, and $s_{\mu\nu i}\equiv c_{\mu i}^\dag c_{\nu i}$ is a transition operator for spin $i$.
We can then consider the addition of, for example, an inhomogeneous magnetic field or Ising couplings,
\begin{align}
  H_{\t{field}} = \sum_i B_i s_{\z,i},
  &&
  H_{\t{Ising}} = \sum_{i\ne j} J_{ij} s_{\z,i} s_{\z,j},
  \label{eq:field_ising}
\end{align}
or more generally an $M$-body operator\footnote{At face value, an $M$-body operator with $M>2$ does not typically appear in nature.
Nonetheless, considering $M>2$ illuminates the structure of eigenstates (and eigenvalues) of $H_0$, and allows us to go to high orders in perturbation theory with single- and two-body perturbations.}
\begin{align}
  \O\p{w,X} = \sum_{k\in\D_N\p{M}} w_k X_k,
\end{align}
where $w$ is a dimension-$M$ (i.e.~$M$-index) tensor of scalar
coefficients $w_k\equiv w_{k_1k_2\cdots k_M}$; $X$ is an $M$-spin
operator, e.g.~$s_\z\otimes s_\z$ in the case of Ising interactions
with $M=2$; $k\equiv\p{k_1,k_2,\cdots,k_M}$ is a list of the
individual spins $k_i\in\ZZ_N\equiv\set{1,2,\cdots,N}$ that the operator $X_k\equiv X_{k_1k_2\cdots k_M}$ acts on; and
\begin{align}
  \D_N\p{M} \equiv
  \set{ k \in \ZZ_N^M : \t{all entries $k_i$ of $k$ are distinct} },
\end{align}
is the strictly ``off-diagonal'' part of $\ZZ_N^M$, which is necessary to identify for a consistent definition of $X_k$ as an $M$-body operator.
In this notation, the magnetic field and Ising Hamiltonians in Eq.~\eqref{eq:field_ising} respectively become $\O\p{B,s_{\z}}$ and $\O\p{J,s_\z\otimes s_\z}$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Three-laser drive with complex amplitudes}
\label{sec:full_drive}

In order to arrive at the single-spin drive Hamiltonian in Eq.~\eqref{eq:drive_single} of the main text, we made the simplifying assumption that all drive amplitudes were real, which essentially enforces a phase-locking condition between the driving lasers.
If the drive amplitudes are complex, $\Omega_m\to\Omega_me^{-\i\eta_m}$ (with real $\Omega_m,\eta_m$), then the single-spin drive Hamiltonian becomes
\begin{multline}
  \Delta \times H_{\t{3LD}}^{\t{single}}
  = \p{\Omega_+^2 - \Omega_-^2} s_\z
  - \sum_{\sigma\in\set{\pm1}} \Omega_0 \Omega_\sigma
  \p{\sigma s_{\tilde\eta_\sigma,\x}
    + s_\z s_{\tilde\eta_\sigma,\x}
    + s_{\tilde\eta_\sigma,\x} s_\z} \\
  - \Omega_0^2 s_\z^2 - \p{\Omega_+ + \Omega_-}^2 s_{\tilde\eta_0,\x}^2
  - \p{\Omega_+ - \Omega_-}^2 s_{\tilde\eta_0,\y}^2,
\end{multline}
where $s_{\eta\alpha} \equiv e^{-\i\eta s_\z} s_\alpha e^{\i\eta s_\z}$ is a rotated spin-$\alpha$ operator (with e.g.~$s_{\pi/2,\x}=s_\y$), and
\begin{align}
  \tilde\eta_\pm \equiv \pm \p{\eta_\pm - \eta_0},
  &&
  \tilde\eta_0 \equiv \f{\eta_+ - \eta_-}{2}.
\end{align}
